Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-11-10 manuscript/text_reuse.tex
updates to the paper

\textit{Alignments}\\
The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences. The same algorithm has been used by \citet{wilkerson2015tracing} to trace bills through the legislative process in congress. When considering two bills, the algorithm treats each bill as a sequence of words and tries to find the best alignment between these two sequences. \citet{wilkerson2015tracing} split the bills into sections and search for text reuse across sections. Since this results in about 7 billion possible pairs, first filter out pairs that don't have an exact match of a sequence of at least ten words. We encounter the same problem in our analysis to a greater extent. Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.

@@

\subsection*{Tasks}

\begin{itemize}
    \item For the 1000 bill sample, retrieve the 100 most similar bills from the database 
    \item Calculate the alignments between the focus bills and the retrieved bills
    \item Assess the relationship of the search score with the alignment scores
\end{itemize}

>>>>

\section{Alignments}

The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences. The same algorithm has been used by \citet{wilkerson2015tracing} to trace bills through the legislative process in congress. When considering two bills, the algorithm treats each bill as a sequence of words and tries to find the best alignment between these two sequences. \citet{wilkerson2015tracing} split the bills into sections and search for text reuse across sections. Since this results in about 7 billion possible pairs, first filter out pairs that don't have an exact match of a sequence of at least ten words. We encounter the same problem in our analysis to a greater extent. Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.

@@

In order to evaluate how well the pre screening algorithms performs we select 1000 focus bills at random and retrieve the 1000 most similar bills according to the lucene score (described above). We then calculate find the best alignments between the sections of the focus bill and the section of each of the retrieved bills. This procedure generates a dataset of approximately 4 million alignments.

For a first assessment of the usefulness of the lucene scores to select document that align well, we investigate the relationship of these scores with the alignment scores. Figure \ref{fig:lu_al_scores} displays the lucene scores against the alignment scores for a random sample of 500,000 alignments. The color indicates if the bills from which the alignment was genrated are from the same state, the larger triangles indicate scores for a bill compared to itself. In order to assess which alignments would get selected if thresholding, that is selecting for example the 100 closest bills according to the lucene score, we plotted all alignments for a sample of 9 focus bills. The green points indicate alignments from the 100 bills with the highest lucene scores for the respective focus bill.

\begin{figure}[ht!]
    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/lu_al_scores.png}}
    \caption{Alignment scores and lucene scores for a sample of 500,000 alignments (sections). The color indicates if the bills of the alignment are from the same state. The larger triangles indicate alignment and lucene scores for sections of bills compared to themselves.}
\label{fig:lu_al_scores} 
\end{figure}

\begin{figure}[ht!]
    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/closest100.png}}
    \caption{Alignment and lucene scores for a sample of nine focus bills (panels). Each point in the plot is an alignment for a section of one comparison bill. The color indicates, if the section comes from a bill that is among the 100 bills with the highest lucene score for the specific focus bill. The large triangles indicate that an alignment is from a comparison of the focus bill with itself.}
\label{fig:closest100} 
\end{figure}

\textit{Identifying procedural alignment text}

Bills share a lot of language that is not related to the policy content of the bill. Especially within states bills have similar headers or formatting content. Further more there is procedural language and common phrases that are used across many, substantively unrelated bills and across states. In order to identify such alignments, we use the fact that we know that within states these matches are so common. We use the following procedure:

For each state:\\
\begin{itemize}
    \item sample n bills
    \item calculate alignments between all sections of these bills
    \item Identify matching alignments with one of the following:
        \begin{itemize}
            \item Perfect string match
            \item length normalized alignment score (threshold?)
            \item String similarity measure (threshold?)
        \end{itemize}
    \item label these alignments as boilerplate
    \item (Optional:) Train classifier on this labeled data
    \item For all alignments found remove the ones that are labeled as boilerplate by the classifier
\end{itemize}
